---
title: "01-data-explore"
output:
  html_document: default
  md_document:
    variant: markdown_github
  pdf_document: default
---

```{r}
library(tidyverse)
```

Reading in Cockle Data csv
```{r}
CockleData <- read.csv("../data/CockleData.csv")
```



Here is a plot

```{r}
ggplot(CockleData, aes(`Width..cm.`,`Height..cm.`,colour=`Male.Grade`,size=`Female.Gonad.Grade`,shape=Location))+geom_point()+
theme_bw()+theme(panel.grid.major = element_blank(),
                panel.grid.minor = element_blank())+scale_colour_brewer(palette = 11)
```
```{r}
ggplot(CockleData, aes(x = Height..cm., y = Female.Gonad.Stage)) +
  geom_point()
```

```

```{r}
ggplot(CockleData, aes(x = Female.Gonad.Stage)) +
  geom_histogram(bins = 30) +
  facet_wrap(~Date)
```
```{r}
ggplot(CockleData, aes(x = Male.Gonad.Stage)) +
  geom_histogram(bins = 30) +
  facet_wrap(~Date)
```



```{r}
ggplot(CockleData, aes(`Width..cm.`,`Male.Grade`,colour=`Male.Grade`,size=`Female.Gonad.Grade`,shape=Location))+geom_point()+
theme_bw()+theme(panel.grid.major = element_blank(),
                panel.grid.minor = element_blank())+scale_colour_brewer(palette = 11) +
  facet_wrap(~Date)
```
```{r}
ggplot(CockleData, aes(`Width..cm.`,`Height..cm.`,colour=`Male.Grade`,size=`Female.Gonad.Grade`,shape=Location ))+geom_point(alpha = 0.5)+
theme_bw()+theme(panel.grid.major = element_blank(),
                panel.grid.minor = element_blank())+scale_colour_brewer(palette = 11) +
  facet_wrap(~Location.Type)
  
```
```{r}
ggplot(CockleData, aes(`Width..cm.`,`Height..cm.`,colour=`Male.Grade`,size=`Female.Gonad.Grade`,shape=Location ))+geom_point(alpha = 0.5)+
theme_bw()+theme(panel.grid.major = element_blank(),
                panel.grid.minor = element_blank())+scale_colour_brewer(palette = 11) +
  facet_wrap(~Date)
  
```



```{r}
ggplot(CockleData, aes(x = Female.Gonad.Stage, y = Male.Gonad.Stage, color = Width..cm.)) +
  geom_point(alpha = .1) +
  geom_jitter(size = 4, width = 0.3, height = 0.5) +
  facet_wrap(~Date)
```

```{r}
ggplot(CockleData, aes(fill=Female.Gonad.Stage, y=Male.Gonad.Stage, x=Date)) + 
    geom_bar(position="stack", stat="identity")
```
