---
title: "03-Histology"
output: html_document
---


```{r}
library(tidyverse)
library(MASS)
```


Reading in Cockle Data csv
```{r}
CockleData <- read.csv("../data/CockleData.csv")
```


Kruskal-Wallis one-way analysis of variance analyzing female gonad grade by date
```{r}
kruskal.test(CockleData$`Female.Gonad.Grade`~CockleData$Date)
```


Kruskal-Wallis one-way analysis of variance analyzing male gonad grade by date
```{r}
kruskal.test(CockleData$`Male.Grade`~CockleData$Date)
```


Ordered Logistic Regression of female gonad grade analyzed by width and height 
```{r}
summary(polr(as.factor(CockleData$`Female.Gonad.Grade`)~CockleData$`Width..cm.`+CockleData$`Height..cm.`,Hess=TRUE))

ctableF <-coef(summary(polr(as.factor(CockleData$`Female.Gonad.Grade`)~CockleData$`Width..cm.`+ CockleData$`Height..cm.`,Hess=TRUE)))

p <- pnorm(abs(ctableF[, "t value"]), lower.tail = FALSE) * 2

(ctableF <- cbind(ctableF, "p value" =p))
```



Making Plots
    
    Figure 7. Date, male and female gonad stage, and width of each basket cockle 
```{r}
ggplot(CockleData, aes(x=`Female.Gonad.Stage`, y=`Male.Gonad.Stage`, color=`Width..cm.`)) +geom_point()+facet_wrap(~Date)+geom_jitter(size=4, width =0.3, height =0.5)+xlab("Female Gonad Stage")+ylab("Male Gonad Stage")+labs(color="Width (cm)")+scale_color_gradient(low="navajowhite1",high="red3")+ theme(strip.background = element_rect( fill="white"),panel.background = element_rect(fill="white"),panel.grid.major = element_line("gray92"),panel.grid.minor = element_line("gray92"),panel.border = element_rect("black",size=0.5,fill=NA), strip.text=element_text(size=10))
```

    Figure 9. Date, male and female gonad stage, and predicted age of each basket cockle
```{r}
ggplot(CockleData, aes(x=`Female.Gonad.Stage`, y=`Male.Gonad.Stage`, color=`Predicted.Age`)) +geom_point()+facet_wrap(~Date)+geom_jitter(size=4, width =0.3, height =0.5)+xlab("Female Gonad Stage")+ylab("Male Gonad Stage")+labs(color="Predicted Age")+theme(strip.background = element_rect( fill="white"),panel.background = element_rect(fill="white"), panel.grid.major = element_line("gray92"), panel.grid.minor = element_line("gray92"),
panel.border = element_rect("black",size=0.5,fill=NA),strip.text=element_text(size=10)) + scale_colour_brewer(palette="RdYlBu") 
```


Reading in female gonad grade vs. size csv
```{r}
SizeRange_FemaleGrade <- read.csv("../data/SizeRange_FemaleGrade.csv")
```

    Figure 8. Female gonad grade vs. size 
```{r}
ggplot(SizeRange_FemaleGrade, aes(fill=Grade, x=`Width.range..cm.`,y=`Number.of.C..nuttallii`))+xlab("Width Range (cm)")+ylab("Number of C. nuttallii")+geom_bar(stat="identity")+scale_fill_brewer(palette="Oranges")+theme_bw()+theme(panel.grid.major = element_blank(),
panel.grid.minor = element_blank())
```